Paper_analyses

### 2023-01-21 Paper_Analyses_subj_obje_arousal.Rmd
missed push
Prep-pub updates

          # surface = FALSE,
          # point.col = ""
          )
```

@@

Do we get the same patterns when loking at paticipants and stimuli searatelly

>>>>

          # surface = FALSE,
          # point.col = ""
          )

pupil_arousal_findings$pupil_from_ar_vale

library(insight)
sjPlot::sjp.lmer(pupil_arousal_findings$pupil_from_ar_vale)

# load packages
devtools::install_cran("sjPlot", force = TRUE, dependencies = TRUE)
install.packages("sjPlot")
library(sjPlot)
library(sjmisc)

@@

Do we get the same patterns when looking at participants and stimuli separately
